An Open Repository of Real-Time COVID-19 Indicators

### 2021-06-21 forecast/paper/paper.tex
Update acks

\acknow{We thank Matthew Biggerstaff, Logan Brooks, Johannes Bracher, Michael 
  Johansson, Evan Ray, Nicholas Reich, and Roni Rosenfeld for several
  enlightening conversations about scoring and evaluation.  The research was  
  supported by gifts from Facebook, Google, McCune, and Optum; 
  Centers for Disease Control and Prevention (CDC) grant U01IP001121; the 
  Canadian Statistical Sciences Institute; National Sciences and Engineering
  Research Council of Canada (NSERC) grant RGPIN-2021-02618; and National
  Science Foundation Graduate Research Fellowship Program (NSF GRFP) award
  DGE175016.}

>>>>

\acknow{We thank Matthew Biggerstaff, Logan Brooks, Johannes Bracher, Michael 
  Johansson, Evan Ray, Nicholas Reich, and Roni Rosenfeld for several
  enlightening conversations about scoring and evaluation.  The research was  
  supported by gifts from Facebook, Google, McCune, and Optum; 
  Centers for Disease Control and Prevention (CDC) grant U01IP001121; the 
  Canadian Statistical Sciences Institute; National Sciences and Engineering
  Research Council of Canada (NSERC) grant RGPIN-2021-02618; and National
  Science Foundation Graduate Research Fellowship Program (NSF GRFP) award
  DGE1745016.}

### 2021-06-21 indicators/paper/paper.tex
Update acks

\acknow{We thank TODO.
  This research was supported by Centers for Disease Control and Prevention
  (CDC) grant U01IP001121, and gifts from Facebook, Google, McCune, and
  Optum.}

>>>>

\acknow{We thank TODO.
  This research was supported by gifts from Facebook, Google, McCune, and
  Optum; Centers for Disease Control and Prevention (CDC) grant U01IP001121;
  National Science Foundation Graduate Research Fellowship Program (NSF GRFP)
  awards DGE1745016; and the Center for Machine Learning and Health (CMLH) at
  Carnegie Mellon University.}
